---
title: "Community analysis"
author: "MNitschke"
date: "18/12/2019"
output: html_document
---

# Libraries

```{r echo = FALSE, message = FALSE}
library(speedyseq)
library(vegan)
library(microbiome)
library(DESeq2)
library(kmer)
library(ape)
library(insect)
library(aphid)
library(Biostrings)
library(phangorn)
library(hiReadsProcessor)
library(DECIPHER)
library(genefilter)
library(alignfigR)
library(bioseq)
library(dada2)
source(file = "../../R/help.R")

library(tidyverse)
library(purrr)
library(scales)
library(ggraph)
library(igraph)
library(tidygraph)
library(ggalt)
library(reshape2)
library(ggsci)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(pander)

theme_set(theme_bw())
```

# Load in phyloseq object

Calculate library stats and clean the data

```{r}
ps <- readRDS("../dada2_Heron/phyloseq.rds") %>%
  subset_samples(Heron_study == "y")

# Use rarefaction curves to investigate the effect of sequencing depth on ASV recovery (remove negative controls here as rarefaction is meaningless on samples that have so few reads) - Note: all samples appear to reach saturation.
p <- phyloseq.extended:::ggrare(ps %>% subset_samples(Type != "x"), step = 100, color = "Type", label = "Sample")
p + facet_wrap(~Type, scales = "free_x") +
  theme(aspect.ratio = 1) +
  xlab("Number of reads") +
  ylab("Number of ASVs") +
  ggtitle(label = "Rarefaction curves")

# Supp plot/summary to show how few samples in summer contained Symbiodiniaceae from the sediment and that they were instead dominated by prorocentrales
sediment_summer <- ps %>% 
  subset_samples(Specific == "Sediment") %>%
  subset_samples(Season == "Summer")
sediment_summer %>% psmelt() %>%
  filter(Abundance > 0) %>%
  mutate(Family = fct_drop(Family)) %>%
  group_by(Sample, Family) %>%
  summarise(sum_abund = sum(Abundance)) %>%
  ungroup() %>%
  group_by(Sample) %>%
  mutate(Abundance_rel = (sum_abund/sum(sum_abund))*100) %>%
  ggplot(aes(x = Sample, y = Abundance_rel)) +
      geom_bar(stat = "identity", aes(fill = Family), position = "fill") + 
      scale_y_continuous(labels = scales::percent) +
      #facet_wrap(~Season, scales = "free_y", ncol = 1) +
      theme(aspect.ratio = 1) +
      guides(fill = guide_legend(ncol = 1)) +
      theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "left") +
      ylab("Relative Abundance (%)")

# Load in phylogenetic tree (see below)
tree <- read_tree("ITS2_28S.tre")
phy_tree(ps) <- phy_tree(tree)

# Library Summary stats
sum(sample_sums(ps)) # = 6498134 before clean

lib_stats <- ps %>% psmelt() %>%
  filter(Family == "Symbiodiniaceae") %>%
  filter(Type != "Culture") %>%
  filter(Abundance > 0) %>%
  group_by(Sample, Season, Type, Specific, Site, Replicate) %>%
  summarise(library_size = sum(Abundance)) %>%
  group_by(Sample, Type, Specific, Site, Replicate) %>%
  arrange(Season, Type, Specific, Site, Replicate, Sample, desc(library_size)) %>%
  mutate(sample_index = group_indices())

# Clean data
ps <- ps %>% # Keep only samples for Heron Island study
  subset_taxa(Family == "Symbiodiniaceae") # Remove ITS2 sequences not assigned to Symbiodiniaceae

sum(sample_sums(ps)) # 2986360 after clean

# Clean up low-depth samples and low-abundance ASVs
ps <- prune_samples(sample_sums(ps) >= 250, ps) # There arent any Symbiodiniaceae sequences in the negative controls (in fact very few sequences at all), and this step removes all negative controls from the dataset.
ps <- prune_taxa(taxa_sums(ps) > 1, ps)
```

# Summary counts

```{r}
ASV_count <- psmelt(ps) %>%
  filter(Type != "Culture") %>%
  filter(Abundance > 0) %>%
  group_by(OTU) %>%
  slice(1)

Genus_count <- psmelt(ps) %>%
  filter(Type != "Culture") %>%
  filter(Abundance > 0) %>%
  group_by(Genus) %>%
  summarise(total = sum(Abundance))

Genus_niche_count <- psmelt(ps) %>%
  filter(Type != "Culture") %>%
  filter(Abundance > 0) %>%
  group_by(Genus, Specific) %>%
  summarise(total = sum(Abundance))

Genus_niche_count <- ps %>%
  psmelt() %>%
  filter(Type != "Culture") %>%
  filter(Abundance > 0) %>%
  group_by(Sample) %>%
  summarise(Gen_count = n_distinct(Genus)) %>%
  ungroup()
```

# Core ASVs in the environment

```{r}
ps_filt <- ps %>%
  subset_samples(Type == "Environment")
ps_filt <- ps_filt %>%
  subset_samples(sample_sums(ps_filt) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_core <- core_members(ps_filt, detection = 0.01, prevalence = 1) # No study-wide core

ps_sed <- ps %>%
  subset_samples(Specific == "Sediment") 
ps_sed <- ps_sed %>%
  subset_samples(sample_sums(ps_sed) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_sed_core <- core_members(ps_sed, detection = 0.01, prevalence = 1) # No sediment core

ps_alg <- ps %>%
  subset_samples(Specific == "Macroalgae") 
ps_alg <- ps_alg %>%
  subset_samples(sample_sums(ps_alg) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_alg_core <- core_members(ps_alg, detection = 0.01, prevalence = 1) # No algae core

ps_water <- ps %>%
  subset_samples(Specific == "Water") 
ps_water <- ps_water %>%
  subset_samples(sample_sums(ps_water) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_water_core <- core_members(ps_water, detection = 0.01, prevalence = 1, include.lowest = TRUE) # "ASV5" - C15_AY239369

# Summary - there is only one core ASV at 100% prevalence for each environmental niche, either indicating seasonality or patchiness.

# Spawning ---------------------------------

ps_filt_spawn <- ps %>%
  subset_samples(Type == "Environment") %>%
  subset_samples(Season == "Spawning")
ps_filt_spawn <- ps_filt_spawn %>%
  subset_samples(sample_sums(ps_filt_spawn) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_core_spawn <- core_members(ps_filt_spawn, detection = 0.01, prevalence = 1, include.lowest = TRUE) # No summer study-wide core

ps_sed_spawn <- ps %>%
  subset_samples(Specific == "Sediment") %>%
  subset_samples(Season == "Spawning") 
ps_sed_spawn <- ps_sed_spawn %>%
  subset_samples(sample_sums(ps_sed_spawn) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_sed_core_spawn <- core_members(ps_sed_spawn, detection = 0.01, prevalence = 1, include.lowest = TRUE) # No summer sediment core

ps_alg_spawn <- ps %>%
  subset_samples(Specific == "Macroalgae") %>%
  subset_samples(Season == "Spawning")
ps_alg_spawn <- ps_alg_spawn %>%
  subset_samples(sample_sums(ps_alg_spawn) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_alg_core_spawn <- core_members(ps_alg_spawn, detection = 0.01, prevalence = 1, include.lowest = TRUE) #  "ASV5" C15_AY239369

ps_water_spawn <- ps %>%
  subset_samples(Specific == "Water") %>%
  subset_samples(Season == "Spawning") 
ps_water_spawn <- ps_water_spawn %>%
  subset_samples(sample_sums(ps_water_spawn) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_water_core_spawn <- core_members(ps_water_spawn, detection = 0.01, prevalence = 1, include.lowest = TRUE) # "ASV13" 	C3*_HM031101, "ASV17" D1_DQ838545, "ASV33" C1_AF195144, "ASV5" C15_AY239369

# Summer ---------------------------------

ps_filt_summer <- ps %>%
  subset_samples(Type == "Environment") %>%
  subset_samples(Season == "Summer")
ps_filt_summer <- ps_filt_summer %>%
  subset_samples(sample_sums(ps_filt_summer) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_core_summer <- core_members(ps_filt_summer, detection = 0.01, prevalence = 1, include.lowest = TRUE) # No summer study-wide core

ps_sed_summer <- ps %>%
  subset_samples(Specific == "Sediment") %>%
  subset_samples(Season == "Summer") 
ps_sed_summer <- ps_sed_summer %>%
  subset_samples(sample_sums(ps_sed_summer) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_sed_core_summer <- core_members(ps_sed_summer, detection = 0.01, prevalence = 1, include.lowest = TRUE) # No summer sediment core

ps_alg_summer <- ps %>%
  subset_samples(Specific == "Macroalgae") %>%
  subset_samples(Season == "Summer")
ps_alg_summer <- ps_alg_summer %>%
  subset_samples(sample_sums(ps_alg_summer) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_alg_core_summer <- core_members(ps_alg_summer, detection = 0.01, prevalence = 1, include.lowest = TRUE) # No summer algae core

ps_water_summer <- ps %>%
  subset_samples(Specific == "Water") %>%
  subset_samples(Season == "Summer") 
ps_water_summer <- ps_water_summer %>%
  subset_samples(sample_sums(ps_water_summer) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)
ps_water_core_summer <- core_members(ps_water_summer, detection = 0.01, prevalence = 1, include.lowest = TRUE) # "ASV5" C15_AY239369

# Summary - C15 signature is detectable in the water column in both Spawning and Summer, however, only during spawning are the C3 and C1 ASVs detectable in all water samples. The C15 sequence is present in all macroalgae samples during spawning also.
```

# Alpha diversity

# Phylogenetically weighted distance matrices

Bring in LSU (28S) distance matrix from Nitschke et al 2020 J. Phycol. These include the latest LSU distances, including Freudenthalidium and Halluxium

```{r}
#Import the model corrected (GTR+G+I) p-distance output from raxML
distnits <- read.table("Nitschke_et_al_Symbiodiniaceae_distances.csv", header = TRUE, sep = ",")

# Import the genus(clade) information for each sequence
genuskey <- read.table("Nitschke_et_al_distances_key.csv", header = TRUE, sep = ",")

# Merge the above data frames
distdf <- left_join(distnits, genuskey, by = c("from" = "seq"))
distdf <- left_join(distdf, genuskey, by = c("to" = "seq"))

# Generate mean inter-genus distances
dist_means <- distdf %>%
  group_by(Genus.x, Genus.y) %>%
  summarise(dist = mean(dist)) %>%
  filter(Genus.x != Genus.y) %>%
  filter(Genus.x != "Outgroup", Genus.y != "Outgroup")
```

Align sequences from each genus and generate intra-genus distances

```{r}
# Function for subsetting phyloseq object
generate_intragenus_dist <- function(ps, genus = "Symbiodinium"){
  taxdf <- as.data.frame(tax_table(ps)@.Data) %>%
    tibble::rownames_to_column(var = "ASVID") %>%
    filter(Genus == genus)
  rownames(taxdf) <- taxdf$ASVID
  taxdf$ASVID <- NULL
  taxdf <- as.matrix(taxdf) %>%
    tax_table()
  phy_subset <- merge_phyloseq(tax_table(taxdf),
                               otu_table(ps, taxa_are_rows = FALSE),
                               refseq(ps),
                               sample_data(ps))
  seqs <- refseq(phy_subset)
  aligned <- AlignSeqs(seqs)
  writeXStringSet(aligned, filepath = paste0(genus,"_aligned.fasta"))
  aligned <- read.alignment(paste0("alignments/",genus,"_aligned.fasta"), format = "fasta")
  dis <- (as.matrix(dist.alignment(aligned, matrix = "identity" )))^2
  saveRDS(dis, paste0("intra_genus_dist/", genus, "-dist.rda"))
}

# List of genera to iterate over
gen_list <- c("Cladocopium", "Halluxium", "Symbiodinium_Fr2", "Freudenthalidium", "Symbiodinium_Fr4", "Fugacium", "Breviolum", "Symbiodinium_I", "Foraminifera_D", "Durusdinium", "Gerakladium", "Effrenium", "Symbiodinium")

# Generate intra-genus distance matrices
for(i in 1:length(gen_list)){
  print(gen_list)[i]
  generate_intragenus_dist(ps, genus = gen_list[i])
}
```

Map in the inter-genus distances and make UPGMA tree

```{r}
ASV_list <- taxa_names(ps)
ASV_matrix <- matrix(0, nrow = length(ASV_list), ncol=length(ASV_list), dimnames = list(ASV_list, ASV_list))
ASV_matrix_melt <- melt(ASV_matrix)

# Load in intra-genus distance paths
intra_dist_paths <- data.frame(path = list.files("intra_genus_dist/", pattern = "-dist")) %>%
    separate(col = path, into = c("start"), sep = "-", extra = "drop", remove = FALSE)

# Loop and update ASV_matrix_melt with intra-genus distances
for(i in 1:length(intra_dist_paths$start)){
  distm <- readRDS(paste0("intra_genus_dist/",intra_dist_paths$path[i]))
  meltdist <- melt(distm)
  ASV_matrix_melt <- left_join(ASV_matrix_melt, meltdist, by = c("Var1", "Var2")) %>%
  mutate(value = case_when(is.na(value.y) ~ value.x, TRUE ~ value.y)) %>%
  select(-value.x, -value.y)
}

ps_long <- psmelt(ps) %>%
  select(OTU, Genus) %>%
  group_by(OTU, Genus) %>%
  distinct()

dist_means_rev <- dist_means %>%
  select(Genus.y, Genus.x, dist) %>%
  rename(Genus.1 = "Genus.y", Genus.2 = "Genus.x")

# Join in the inter-genus distances
final_long_dist <- left_join(ASV_matrix_melt, ps_long, by = c("Var1" = "OTU")) %>%
  left_join(., ps_long, by = c("Var2" = "OTU")) %>%
  left_join(., dist_means) %>%
  left_join(., dist_means_rev, by = c("Genus.x" = "Genus.1", "Genus.y" = "Genus.2")) %>% # sTUCK HERE
  mutate(final_value = case_when(is.na(dist.y) ~ dist.x, TRUE ~ dist.y)) %>%
  mutate(final_value = case_when(is.na(final_value) ~ value, TRUE ~ final_value)) %>%
  select(Var1, Var2, value = final_value)

# Create master distance matrix
master_dist <- reshape2::acast(final_long_dist, Var1 ~ Var2, value.var = 'value')
dim(master_dist)

# UPGMA tree
tree <- phangorn::upgma(master_dist)
write.tree(tree, file = "ITS2_28S.tre")

# Update ps object
## phy_tree(ps) <- phy_tree(tree)
```

Simpler, alignment-free method

-- Note the below produces almost identical results in the unifrac distance-based PCoA ordinations as the ITS2+28S UPGMA tree above 

```{r}
ASVs <- refseq(ps) %>%
    DNAStringSet_to_df()
  
kdist <- ASVs %>%
  df_to_DNAStringset() %>%
  DNAStringSet_to_DNAbin() %>%
  kdistance(k = 7, residues = "DNA", method = "edgar") %>%
  as.matrix()

tree <- phangorn::upgma(kdist)
write.tree(tree, file = "ITS2_kmer.tre")

# Update ps object
## phy_tree(ps) <- phy_tree(tree)
```

Inspect the differences in the two trees

```{r}
ITS2_28S_tree <- read.tree("ITS2_28S.tre")
ITS2_kmer_tree <- read.tree("ITS2_kmer.tre")

dnd1 <- as.dendrogram(ITS2_28S_tree)
dnd2 <- as.dendrogram(ITS2_kmer_tree)
dndlist <- dendextend::dendlist(dnd1, dnd2)
dendextend::tanglegram(dndlist, fast = TRUE, margin_inner = 5)
```

# Figure 1

## Barplot

```{r}
glom <- tax_glom(ps, taxrank = "Genus") %>%
  transform_sample_counts(function(x) x/sum(x)) %>%
  psmelt() %>%
  filter(str_detect(Type, "Host|Environment")) %>%
  mutate(Genus = fct_relevel(Genus, c("Cladocopium", "Halluxium", "Symbiodinium_Fr2", "Freudenthalidium", "Symbiodinium_Fr4", "Fugacium", "Breviolum", "Symbiodinium_I", "Foraminifera_D", "Durusdinium", "Gerakladium", "Effrenium", "Symbiodinium")),
         Specific = fct_relevel(Specific, c("Acropora aspera", "Montipora digitata", "Pocillopora damicornis", "Water", "Sediment", "Macroalgae"))) %>%
  filter(Abundance > 0) %>%
  mutate(Genus = fct_drop(Genus)) %>%
  group_by(Type, Specific, Genus, Season) %>%
  summarise(mean_abund = mean(Abundance))

genus_palette <- pal_d3(palette = "category20")
genus_cols <- as.vector(genus_palette(length(levels(glom$Genus))))
names(genus_cols) <- levels(glom$Genus)

pb <- ggplot(data = glom, aes(x = Specific, y = mean_abund)) +
      geom_bar(stat = "identity", aes(fill = Genus), position = "fill") + 
      scale_y_continuous(labels = scales::percent) +
      facet_wrap(~Season, scales = "free_y", ncol = 1) +
      theme(aspect.ratio = 1, legend.position = "right") +
      guides(fill = guide_legend(ncol = 1)) +
      theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "left") +
      scale_fill_manual(values = genus_cols) +
      ylab("Relative Abundance (%)")
```

## PCoA

```{r}
ps_filt <- ps %>%
  subset_samples(Type != "Culture") %>%
  subset_samples(Type != "Host") %>%
  subset_samples(sample_sums(ps) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)

# Hellinger transform (square root of relative abundances)
ps.hell <- microbiome::transform(ps_filt, transform = "hellinger", target = "OTU", shift = 1, scale = 1)

# Produce NMDS ordination of bray curtis dissimilarity matrix
ps.uni <- ordinate(ps.hell, "PCoA", "unifrac", weighted = TRUE)

# Facet by sample vs taxa (biplot)
po <- plot_ordination(ps.hell, ps.uni, justDF = TRUE) %>%
  mutate(Specific = fct_relevel(Specific, c( "Water", "Sediment", "Macroalgae"))) %>%
  mutate(encircle = paste(Specific, "_", Season)) %>%
  ggplot(aes(x = Axis.1, y = Axis.2)) +
  geom_point(size = 3, aes(colour = Specific, shape = Season)) +
  geom_encircle(aes(fill = encircle), s_shape = 1, expand = 0, alpha = 0.2, show.legend = FALSE) +
  theme(aspect.ratio = 1) +
  scale_colour_manual(values = c("#1F77B4FF", "#FF7F0EFF", "#2CA02CFF")) +
  scale_fill_manual(values = c("#1F77B4FF", "#1F77B4FF", "#FF7F0EFF", "#FF7F0EFF", "#2CA02CFF", "#2CA02CFF"))
```

```{r}
library(patchwork)
pb + po
```

# Multivariate analyses

## PERMANOVA and betadisper on weighted unifrac distances

```{r}
wuni <- phyloseq::distance(ps.hell, method = "unifrac", weighted = TRUE)
sampledf <- data.frame(sample_data(ps.hell))

adonis(wuni ~ Specific * Site * Season, data = sampledf)

# Call:
# adonis(formula = wuni ~ Specific * Site * Season, data = sampledf) 
# 
# Permutation: free
# Number of permutations: 999
# 
# Terms added sequentially (first to last)
# 
#                      Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)    
# Specific              5    3.4376 0.68752 20.4815 0.48436  0.001 ***
# Site                  2    0.1556 0.07782  2.3182 0.02193  0.033 *  
# Season                1    0.1349 0.13487  4.0177 0.01900  0.009 ** 
# Specific:Site         4    0.2370 0.05925  1.7651 0.03339  0.059 .  
# Specific:Season       5    0.7230 0.14460  4.3077 0.10187  0.001 ***
# Site:Season           2    0.1825 0.09124  2.7181 0.02571  0.020 *  
# Specific:Site:Season  3    0.1454 0.04848  1.4441 0.02049  0.182    
# Residuals            62    2.0812 0.03357         0.29324           
# Total                84    7.0972                 1.00000           
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

betaspecific <- betadisper(wuni, sampledf$Specific)
anova(betaspecific)

# Analysis of Variance Table
# 
# Response: Distances
#           Df  Sum Sq  Mean Sq F value    Pr(>F)    
# Groups     5 0.94034 0.188068  17.248 1.672e-11 ***
# Residuals 79 0.86138 0.010904                      
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

TukeyHSD(betaspecific)

# Tukey multiple comparisons of means
#     95% family-wise confidence level
# 
# Fit: aov(formula = distances ~ group, data = df)
# 
# $group
#                                                    diff         lwr         upr     p adj
# Macroalgae-Acropora aspera                 0.1701174461  0.04419703  0.29603786 0.0022915
# Montipora digitata-Acropora aspera        -0.0032267834 -0.15572398  0.14927042 0.9999999
# Pocillopora damicornis-Acropora aspera    -0.0001780181 -0.15267522  0.15231918 1.0000000
# Sediment-Acropora aspera                   0.3041059633  0.17203952  0.43617241 0.0000000
# Water-Acropora aspera                      0.1646308838  0.03944257  0.28981920 0.0032526
# Montipora digitata-Macroalgae             -0.1733442295 -0.29926465 -0.04742381 0.0017775
# Pocillopora damicornis-Macroalgae         -0.1702954642 -0.29621588 -0.04437505 0.0022598
# Sediment-Macroalgae                        0.1339885172  0.03377822  0.23419881 0.0026267
# Water-Macroalgae                          -0.0054865623 -0.09644078  0.08546766 0.9999755
# Pocillopora damicornis-Montipora digitata  0.0030487653 -0.14944843  0.15554596 0.9999999
# Sediment-Montipora digitata                0.3073327466  0.17526630  0.43939919 0.0000000
# Water-Montipora digitata                   0.1678576672  0.04266935  0.29304598 0.0025317
# Sediment-Pocillopora damicornis            0.3042839814  0.17221753  0.43635043 0.0000000
# Water-Pocillopora damicornis               0.1648089019  0.03962059  0.28999722 0.0032083
# Water-Sediment                            -0.1394750794 -0.23876388 -0.04018628 0.0013399

betaseason <- betadisper(wuni, sampledf$Season)
anova(betaseason)

# Analysis of Variance Table
# 
# Response: Distances
#           Df  Sum Sq   Mean Sq F value Pr(>F)
# Groups     1 0.00068 0.0006813  0.0222 0.8818
# Residuals 83 2.54170 0.0306229                  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

# Summary: Clearly there is difference around the centroids because the host sample compositions are basically uniform compared to the environmental samples. What about if we subset to just environmental samples and then try? Sediment looks less variable than water and macroalgae.

#---------------------------------------------------------------------

ps_filt_env <- ps %>%
  subset_samples(Type != "Culture") %>%
  subset_samples(Type != "Host") %>%
  subset_samples(sample_sums(ps) > 0) %>%
  filter_taxa(function(x) sum(x) > 0, TRUE)

ps.hell_env <- microbiome::transform(ps_filt_env, transform = "hellinger", target = "OTU", shift = 1, scale = 1)
wuni_env <- phyloseq::distance(ps.hell_env, method = "unifrac", weighted = TRUE)
sampledf <- data.frame(sample_data(ps.hell_env))

adonis_output <- adonis(wuni_env ~ Specific * Site * Season, data = sampledf)

# Call:
# adonis(formula = wuni_env ~ Specific * Site * Season, data = sampledf) 
# 
# Permutation: free
# Number of permutations: 999
# 
# Terms added sequentially (first to last)
# 
#                      Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)    
# Specific              2    1.7363 0.86814 18.3639 0.32186  0.001 ***
# Site                  2    0.1556 0.07782  1.6461 0.02885  0.093 .  
# Season                1    0.1929 0.19288  4.0801 0.03576  0.010 ** 
# Specific:Site         4    0.2307 0.05769  1.2203 0.04277  0.253    
# Specific:Season       2    0.6710 0.33549  7.0966 0.12438  0.001 ***
# Site:Season           2    0.1825 0.09124  1.9300 0.03383  0.053 .  
# Specific:Site:Season  3    0.1454 0.04848  1.0254 0.02696  0.390    
# Residuals            44    2.0801 0.04727         0.38559           
# Total                60    5.3945                 1.00000           
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

adonis_output$aov.tab %>%
  tibble::rownames_to_column(var = "Factor") %>%
  gt::gt()

betaspecific_env <- betadisper(wuni_env, sampledf$Specific)
anova(betaspecific_env) # Still difference between specific niches

# Analysis of Variance Table
# 
# Response: Distances
#           Df  Sum Sq  Mean Sq F value   Pr(>F)   
# Groups     2 0.22107 0.110534  7.4679 0.001301 **
# Residuals 58 0.85848 0.014801                    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

TukeyHSD(betaspecific_env) # Season effect in sediment is driving the larger centroids

# Tukey multiple comparisons of means
#     95% family-wise confidence level
# 
# Fit: aov(formula = distances ~ group, data = df)
# 
# $group
#                            diff         lwr         upr     p adj
# Sediment-Macroalgae  0.13393161  0.03778316  0.23008007 0.0040084
# Water-Macroalgae    -0.00551374 -0.09278130  0.08175382 0.9873508
# Water-Sediment      -0.13944535 -0.23470966 -0.04418104 0.0024017

betaseason_env <- betadisper(wuni_env, sampledf$Season)
anova(betaseason_env) # Still difference between specific niches

# Analysis of Variance Table
# 
# Response: Distances
#           Df  Sum Sq  Mean Sq F value Pr(>F)
# Groups     1 0.00618 0.006184  0.2467 0.6213
# Residuals 59 1.47915 0.025070
```

## Sensitivity analysis

Specific and season are the two main factors explaining the variance in the weighted unifrac distances. Because we have an unbalanced desgin due to poor sequencing depth in a number of samples (and because specific niche had heterogeneity of dispersion), we need to randomly subsample all groups to the smallest group size and run the adonis on each subsample, i.e. bootstrapping.

```{r}
# Bootstrap on ps.hell (includes host samples)

n <- 100
minsamp <- 4 # Only 4 samples from sediment in Summer

F_list_Specific <- list()
R2_list_Specific <- list()
P_list_Specific <- list()

F_list_Season <- list()
R2_list_Season <- list()
P_list_Season <- list()

F_list_interaction <- list()
R2_list_interaction <- list()
P_list_interaction <- list()

for(n in 1:n){
  samptab <- meta(ps.hell) %>% 
  group_by(Specific, Season) %>% 
  sample_n(size = minsamp)

  ps_sub <- subset_samples(ps.hell, ps.hell@sam_data$Sample_ID %in% samptab$Sample_ID)

  set.seed(1234)
  wuni <- phyloseq::distance(ps_sub, method = "unifrac", weighted = TRUE)
  metadata <- meta(ps_sub)
  ado <- adonis(wuni ~ Specific * Season, data = metadata)
  set.seed(NULL)

  F_list_Specific[[n]] <- ado$aov.tab$F.Model[1]
  R2_list_Specific[[n]] <- ado$aov.tab$R2[1]
  P_list_Specific[[n]] <- ado$aov.tab$`Pr(>F)`[1]
    F_list_Season[[n]] <- ado$aov.tab$F.Model[2]
  R2_list_Season[[n]] <- ado$aov.tab$R2[2]
  P_list_Season[[n]] <- ado$aov.tab$`Pr(>F)`[2]
    F_list_interaction[[n]] <- ado$aov.tab$F.Model[3]
  R2_list_interaction[[n]] <- ado$aov.tab$R2[3]
  P_list_interaction[[n]] <- ado$aov.tab$`Pr(>F)`[3]
  print(n)
}

ado_F_specific <- do.call(rbind, F_list_Specific)
ado_R2_specific <- do.call(rbind, R2_list_Specific)
ado_P_specific <- do.call(rbind, P_list_Specific)
ado_F_season <- do.call(rbind, F_list_Season)
ado_R2_season <- do.call(rbind, R2_list_Season)
ado_P_season <- do.call(rbind, P_list_Season)
ado_F_interaction <- do.call(rbind, F_list_interaction)
ado_R2_interaction <- do.call(rbind, R2_list_interaction)
ado_P_interaction <- do.call(rbind, P_list_interaction)

ado_stats_all <- do.call(cbind, list(ado_F_specific, ado_R2_specific, ado_P_specific, ado_F_season, ado_R2_season, ado_P_season, ado_F_interaction, ado_R2_interaction, ado_P_interaction))

# ------------------------------------
# Bootstrap on env only (excludes host samples)

n <- 100
minsamp <- 4 # Only 4 samples from sediment in Summer

F_list_Specific <- list()
R2_list_Specific <- list()
P_list_Specific <- list()

F_list_Season <- list()
R2_list_Season <- list()
P_list_Season <- list()

F_list_interaction <- list()
R2_list_interaction <- list()
P_list_interaction <- list()

for(n in 1:n){
  samptab <- meta(ps.hell) %>% 
  group_by(Specific, Season) %>% 
  sample_n(size = minsamp)

  ps_sub <- subset_samples(ps.hell_env, ps.hell@sam_data$Sample_ID %in% samptab$Sample_ID)

  set.seed(4321)
  wuni <- phyloseq::distance(ps_sub, method = "unifrac", weighted = TRUE)
  metadata <- meta(ps_sub)
  ado <- adonis(wuni ~ Specific * Season, data = metadata)
  set.seed(NULL)

  F_list_Specific[[n]] <- ado$aov.tab$F.Model[1]
  R2_list_Specific[[n]] <- ado$aov.tab$R2[1]
  P_list_Specific[[n]] <- ado$aov.tab$`Pr(>F)`[1]
    F_list_Season[[n]] <- ado$aov.tab$F.Model[2]
  R2_list_Season[[n]] <- ado$aov.tab$R2[2]
  P_list_Season[[n]] <- ado$aov.tab$`Pr(>F)`[2]
    F_list_interaction[[n]] <- ado$aov.tab$F.Model[3]
  R2_list_interaction[[n]] <- ado$aov.tab$R2[3]
  P_list_interaction[[n]] <- ado$aov.tab$`Pr(>F)`[3]
  print(n)
}

ado_F_specific <- do.call(rbind, F_list_Specific)
ado_R2_specific <- do.call(rbind, R2_list_Specific)
ado_P_specific <- do.call(rbind, P_list_Specific)
ado_F_season <- do.call(rbind, F_list_Season)
ado_R2_season <- do.call(rbind, R2_list_Season)
ado_P_season <- do.call(rbind, P_list_Season)
ado_F_interaction <- do.call(rbind, F_list_interaction)
ado_R2_interaction <- do.call(rbind, R2_list_interaction)
ado_P_interaction <- do.call(rbind, P_list_interaction)

ado_stats_env <- do.call(cbind, list(ado_F_specific, ado_R2_specific, ado_P_specific, ado_F_season, ado_R2_season, ado_P_season, ado_F_interaction, ado_R2_interaction, ado_P_interaction))

colnames(ado_stats_env) <- c("F_niche", "R2_niche", "P_niche", "F_season", "R2_season", "P_nseason",  "F_interaction", "R2_interaction", "P_interaction")

write_csv(as.data.frame(ado_stats_env), "bootstrap_env_niche_season_interaction.csv")
```

# Host-derived DIVs

## Mothur scripts

```{r}
make.contigs(inputdir=fastq, file=stability.files)
screen.seqs(inputdir=fastq, fasta=stability.trim.contigs.fasta, maxambig=0, maxhomop=5, group=stability.contigs.groups)
unique.seqs(inputdir=fastq, fasta=stability.trim.contigs.good.fasta)
count.seqs(inputdir=fastq, name=stability.trim.contigs.good.names, group=stability.contigs.good.groups, compress=f)
```

## Import Symportal DIV sequences

```{r}
DIVs <- c("C15","C15dq","C15dr","C15ch","C42a","C1","C42.2","C1b","C1j","C1au","C50b","C50p","C3","C50f","C3bm","C3dt")

postmed <- read_fasta("../../R/symportal_output/post_med_seqs/88_20191231_2020-01-01_01-40-49.793978.seqs.fasta") %>% as_tibble.bioseq_dna() %>% filter(label %in% DIVs)
```

## Import the mothur count table

```{r}
counts <- read.delim("fastq/stability.trim.contigs.good.count_table")

# Remove singletons and doublets
length(counts$Representative_Sequence) # 539058
countsfilt <- counts %>%
  filter(total > 2)
length(countsfilt$Representative_Sequence) # 67496

uniques <- read_fasta("fastq/stability.trim.contigs.good.unique.fasta") %>% 
  as_tibble.bioseq_dna() %>% 
  mutate(label = word(label, 1, sep = "\t")) %>%
  filter(label %in% countsfilt$Representative_Sequence) %>% # filter out singleton and doublet seqs
  mutate(length = str_length(sequence)) %>%
  filter(length %in% (184:310)) # Do min-length filtering to match symportal qc

countsfilt <- countsfilt %>%
  filter(Representative_Sequence %in% uniques$label) %>%
  select(-total) %>%
  left_join(., uniques %>% select(label, sequence), by = c("Representative_Sequence" = "label")) %>%
  mutate(sequence = as.character(sequence))

countsdiv <- data_frame()
for(i in 1:length(DIVs)){
  res <- countsfilt %>% filter(str_detect(sequence, paste0(postmed$sequence[i]))) %>%
    mutate(DIV = paste0(postmed$label[i]))
  countsdiv <- rbind(countsdiv, res)
}

length(unique(countsdiv$DIV)) # All DiVs found

# Exact matching to DIV sequences
countstax <- countsfilt %>%
  filter(!(Representative_Sequence %in% countsdiv$Representative_Sequence)) %>%
  tibble::column_to_rownames(var = "sequence") %>%
  select(-Representative_Sequence) %>%
  t()
```

## Assign taxonomy using RDP classifier

```{r}
tax_bs <- assignTaxonomy(countstax, "ITS2dbn1_Dinophy_Symbio.fasta", multithread = TRUE, outputBootstraps = TRUE, minBoot = 0)
saveRDS(tax_bs, "tax_bs.rds")

tax_bs <- readRDS("tax_bs.rds")
taxa <- as.data.frame(tax_bs$tax, stringsAsFactors = FALSE)
taxa <- tibble::rownames_to_column(taxa, var = "seq")

boot <- as.data.frame(tax_bs$boot)
boot <- tibble::rownames_to_column(boot, var = "seq")

taxfilt <- left_join(taxa, boot, by = "seq", suffix = c("tax", "boot")) %>%
  mutate(Genustax = case_when(Familyboot < 50 & str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                            TRUE ~ as.character(.$Genustax)),
         Speciestax = case_when(Familyboot < 50 & str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                            TRUE ~ as.character(.$Speciestax)),
         Familytax = case_when(Familyboot < 50 & str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                            TRUE ~ as.character(.$Familytax))) %>%
  mutate(Phylumtax = case_when(Phylumboot < 50  & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                               TRUE ~ as.character(.$Phylumtax)),
         Classtax = case_when(Classboot < 50 & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                              TRUE ~ as.character(.$Classtax)),
         Ordertax = case_when(Orderboot < 50 & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                              TRUE ~ as.character(.$Ordertax)),
         Familytax = case_when(Familyboot < 50 & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                               TRUE ~ as.character(.$Familytax)),
         Genustax = case_when(Genusboot < 50 & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                              TRUE ~ as.character(.$Genustax)),
         Speciestax = case_when(Speciesboot < 50 & !str_detect(Familytax, "Symbiodiniaceae") ~ "Unassigned",
                                TRUE ~ as.character(.$Speciestax)))

tax_sym <- taxfilt %>% filter(Familytax == "Symbiodiniaceae")

countssym <- countsfilt %>%
  filter(sequence %in% tax_sym$seq) %>%
  mutate(DIV = NA)

count_final <- rbind(countsdiv, countssym) %>%
  left_join(., tax_sym %>% select(seq, Genustax, Speciestax), by = c("sequence" = "seq"))
```

## Figure 2

```{r}
metadata <- read.csv("metadata.csv") %>%
  select(Sample_ID, Type, Specific, Season, Site, Replicate) %>%
  mutate(Sample_ID = str_remove(Sample_ID, "Re")) %>%
  mutate(label = paste0(Site, ".", Replicate))

count_long <- count_final %>%
  pivot_longer(X1:X74, names_to = "sample", values_to = "abundance") %>%
  mutate(sample = str_remove(sample, "X"),
         sample = paste0(sample, "_ITS2")) %>%
  mutate(DIV = case_when(is.na(DIV) & Genustax == "Cladocopium" ~ "Non-DIV Cladocopium sequences",
                         is.na(DIV) & Genustax != "Cladocopium" ~ "Other Symbiodiniaceae", TRUE ~ DIV)) %>%
    filter(abundance > 0) %>%
  left_join(., metadata, by = c("sample" = "Sample_ID")) %>%
  mutate(DIV = fct_relevel(DIV, c("C50b","C50p","C3","C50f","C3bm","C3dt", "C15","C15dq","C15dr","C15ch", "C42a","C1","C42.2","C1b","C1j","C1au", "Non-DIV Cladocopium sequences", "Other Symbiodiniaceae"))) %>%
  filter(str_detect(Type, "Host|Environment")) %>%
  mutate(Specific = fct_relevel(Specific, c("Acropora aspera", "Water", "Montipora digitata",  "Sediment", "Pocillopora damicornis", "Macroalgae")))

summarystats <- count_long %>%
  group_by(sample, Specific, Season) %>%
  summarise(abund = sum(abundance)) %>%
  arrange(desc(abund))

sample_sums <- count_long %>%
  group_by(sample, Season, Site, Specific) %>%
  summarise(sum_abund = sum(abundance)) %>%
  arrange(Season, sample, Specific, Site)

c3divprofile <- c("C50b","C50p","C3","C50f","C3bm","C3dt")
c15divprofile <- c("C15","C15dq","C15dr","C15ch")
c1divprofile <- c("C42a","C1","C42.2","C1b","C1j","C1au")

c3collection <- count_long %>%
  filter(DIV %in% c3divprofile) %>%
  select(sample, Specific, Season, Site, Replicate, DIV, abundance) %>%
  group_by(sample, Specific, Season, Site, Replicate, DIV) %>%
  summarise(abund = sum(abundance)) %>%
  pivot_wider(names_from = DIV, values_from = abund) %>%
  arrange(Season, Specific, Site, Replicate, sample)

c15collection <- count_long %>%
    filter(Type != "Host") %>%
  filter(DIV %in% c15divprofile) %>%
  select(sample, Specific, Season, Site, Replicate, DIV, abundance) %>%
  group_by(sample, Specific, Season, Site, Replicate, DIV) %>%
  summarise(abund = sum(abundance)) %>%
  pivot_wider(names_from = DIV, values_from = abund) %>%
  arrange(Season, Specific, Site, Replicate, sample)

c1collection <- count_long %>%
    filter(Type != "Host") %>%
  filter(DIV %in% c1divprofile) %>%
  select(sample, Specific, Season, Site, Replicate, DIV, abundance) %>%
  group_by(sample, Specific, Season, Site, Replicate, DIV) %>%
  summarise(abund = sum(abundance)) %>%
  pivot_wider(names_from = DIV, values_from = abund) %>%
  arrange(Season, Specific, Site, Replicate, sample)

# Need to make palettes for each DIV
C3_pal <- c("#006128", "#007028", "#008E28", "#2DC959", "#7BFFA0", "#C9FFCF")
names(C3_pal) <- c("C50b","C50p","C3","C50f","C3bm","C3dt")
C15_pal <- c("#A155B9", "#F765A3", "#FFA4B6", "#F9D1D1")
names(C15_pal) <- c("C15","C15dq","C15dr","C15ch")
C1_pal <- c("#9F3200", "#D44800", "#E9692C", "#ED8756", "#F2A580", "#F6C3AB")
names(C1_pal) <- c("C42a","C1","C42.2","C1b","C1j","C1au")
other_pal <- c("lightblue", "grey75")
names(other_pal) <- c("Non-DIV Cladocopium sequences", "Other Symbiodiniaceae")
pal <- c(C15_pal, C1_pal, C3_pal, other_pal)

# Figure 2
count_long %>%
  ungroup() %>%
  group_by(sample, Specific, Season, label, DIV) %>%
  summarise(abundance = sum(abundance)) %>%
  ungroup() %>%
  ggplot(aes(x = label, y = abundance)) +
    geom_bar(stat = "identity", aes(fill = DIV), position = "fill") +
    facet_wrap(~Specific * Season, scales = "free_x", ncol = 4) +
    scale_y_continuous(labels = scales::percent) +
    theme(aspect.ratio = 1, legend.position = "left") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    scale_fill_manual(values = pal) +
    ylab("Relative Abundance (%)")
```

## Cladocopium summary statistics

```{r}
Clado_ss <- bardf %>%
  filter(Abundance > 0) %>%
  group_by(Sample) %>%
  mutate(Abundance_rel = (Abundance/sum(Abundance))*100) %>%
  ungroup() %>% # Stop here for just ASV relative abundance, continue for DIV vs ASV rel abund
  mutate(ASV_Species = as.character(ASV_Species),
    group = case_when(str_detect(ASV_Species, "ASV") ~ "DIV", TRUE ~ ASV_Species)) %>%
  group_by(Sample, Specific, Season, group) %>%
  summarise(abund = sum(Abundance_rel))
```

# Culture-based DIVs

```{r}
# Symbiodinium start ------------------------
culture_DIV <- ps %>%
  subset_samples(Type == "Culture")
Symbiodinium_DIV <- culture_DIV %>%
  subset_samples(Culture_genus == "Symbiodinium")
Symbiodinium_DIV <- Symbiodinium_DIV %>%
  subset_samples(sample_sums(culture_DIV) > 0)
Symbiodinium_DIV <- Symbiodinium_DIV %>%
  subset_taxa(Genus == "Symbiodinium") %>%
  filter_taxa(function(x) sum(x) > 1, TRUE) # Remove singletons
Symbiodinium_DIV <- transform_sample_counts(Symbiodinium_DIV, function(x) x/sum(x)*100) # Convert to relative abundance

# Top 3 DIVs per culture
Symbiodinium_top_3_ASV <- psmelt(Symbiodinium_DIV) %>%
  group_by(Sample) %>%
  top_n(3, wt = Abundance) %>%
  arrange(Sample, desc(Abundance)) %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|")

CCMP_2430_pal <- c("#DF0000", "#EF7F7F", "#F7BFBF")
names(CCMP_2430_pal) <- c("ASV34|A3_DQ838546", "ASV203|A3_DQ838546", "ASV1006|A3_DQ838546")

CCMP_2461_pal <- c("#FF545E", "#FFA9AE", "#FFD4D7")
names(CCMP_2461_pal) <- c("ASV24|A_AF184942", "ASV712|A_AF184942", "ASV965|A_AF184942")

CCMP_2469_pal <- c("#FF7B00", "#FFBD7F", "#FFDEBF")
names(CCMP_2469_pal) <- c("ASV32|A1.1_AF333504", "ASV234|A1.1_AF333504", "ASV301|A1.1_AF333504")

CCMP_2548_pal <- c("#FFB31F", "#F8FF84", "#FBFFC2")
names(CCMP_2548_pal) <- c("ASV18|A_AF184948", "ASV471|A_AF184948", "ASV436|A_AF184948")

Cult_24_Sugget_pal <- c("#F8FF84")
names(Cult_24_Sugget_pal) <- c("ASV510|A_AF184948")

CCMP_2592_pal <- c("#FF7FC1", "#FFBFE0", "#FFDFEF")
names(CCMP_2592_pal) <- c("ASV28|A5_AF333508", "ASV472|A5_AF333508", "ASV668|A5_AF333508")

Cult_28_Sugget_pal <- c("#FF00FF", "#FF7FFF", "#FFBFFF")
names(Cult_28_Sugget_pal) <- c("ASV39|A_DQ174724", "ASV41|A_DQ174724", "ASV520|A_DQ174724")

Cult_29_Sugget_pal <- c("#8C00A9", "#C57FD4", "#E2BFE9")
names(Cult_29_Sugget_pal) <- c("ASV29|A1_AB097463", "ASV163|A1_AB097463", "ASV341|A1_AB097463")

# Symbiodinium end -------------------------

# Durusdinium start ------------------------

Durusdinium_DIV <- culture_DIV %>%
  subset_samples(Culture_genus == "Durusdinium")
Durusdinium_DIV <- Durusdinium_DIV %>%
  subset_samples(sample_sums(Durusdinium_DIV) > 0)
Durusdinium_DIV <- Durusdinium_DIV %>%
  subset_taxa(Genus == "Durusdinium") %>%
  filter_taxa(function(x) sum(x) > 1, TRUE) # Remove singletons
Durusdinium_DIV <- transform_sample_counts(Durusdinium_DIV, function(x) x/sum(x)*100) # Convert to relative abundance

# Are the top DIVs in the D1a cultures the D1 and D4 sequences sensu LaJeunesse et al 2019 Phycologia?
seqs <- refseq(Durusdinium_DIV) %>%
  DNAStringSet_to_DNAbin() %>%
  bioseq::as_dna() %>%
  as_tibble.bioseq_dna()

symportal <- bioseq::read_fasta("../../Raw_data/Reference_databases/published_div.fasta.gz") %>%
  as_tibble.bioseq_dna()

symportal_D1 <- symportal %>% filter(label == "D1") # Yes 
symportal_D4 <- symportal %>% filter(label == "D4") # Yes

D1 <- seqs %>%
  filter(str_detect(sequence, paste0(symportal_D1$sequence)))
D4 <- seqs %>%
  filter(str_detect(sequence, paste0(symportal_D4$sequence)))

# Top 3 DIVs per culture
Durusdinium_top_3_ASV <- psmelt(Durusdinium_DIV) %>%
  group_by(Sample) %>%
  top_n(3, wt = Abundance) %>%
  arrange(Sample, desc(Abundance)) %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|")

Durusdinium_pal <- c("#0B009F", "#1400D3", "#3F7EFF", "#8BD2FF", "#BFF5FF")
names(Durusdinium_pal) <- c("ASV17|D1_DQ838545", "ASV36|D1a_AF499802", "ASV102|D4-5_EU812743", "ASV251|D1a_AF499802", "ASV117|D1a_AF499802")

# Dursdinium end --------------------------

# Fugacium start ------------------------

Fugacium_DIV <- culture_DIV %>%
  subset_samples(Culture_genus == "Fugacium")
Fugacium_DIV <- Fugacium_DIV %>%
  subset_samples(sample_sums(Fugacium_DIV) > 0)
Fugacium_DIV <- Fugacium_DIV %>%
  subset_taxa(Genus == "Fugacium") %>%
  filter_taxa(function(x) sum(x) > 1, TRUE) # Remove singletons
Fugacium_DIV <- transform_sample_counts(Fugacium_DIV, function(x) x/sum(x)*100) # Convert to relative abundance

# Top 3 DIVs per culture
Fugacium_top_3_ASV <- psmelt(Fugacium_DIV) %>%
  group_by(Sample) %>%
  top_n(3, wt = Abundance) %>%
    arrange(Sample, desc(Abundance)) %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|")

CCMP_2434_pal <- c("#8DFF03", "#C6FF81", "#E8FFCD")
names(CCMP_2434_pal) <- c("ASV15|F_AF333516", "ASV25|F_AF333516", "ASV457|F_AF333516")

Cult_133_pal <- c("#00CF12", "#7FE788", "#CCF5D0")
names(Cult_133_pal) <- c("ASV19|F1_AF184946", "ASV299|F1_AF184946", "ASV405|F1_AF184946")

Cult_135_pal <- c("#7FC98F", "#CCE9D2")
names(Cult_135_pal) <- c("ASV334|F_AF333516", "ASV953|F_AF333516")

# Fugacium end --------------------------

# Filter DIVs into dataframes and others into dataframes

env_ps <- ps %>%
  subset_samples(Type != "Host")

env_ps <- env_ps %>%
  subset_samples(sample_sums(env_ps) > 0)

# DIVs

symbio_DIVs <- psmelt(env_ps) %>%
  filter(!str_detect(Culture_genus, "Breviolum|Cladocopium|Effrenium")) %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|") %>%
  filter(ASV_Species %in% Symbiodinium_top_3_ASV$ASV_Species) %>%
  mutate(ASV_Species = fct_drop(ASV_Species))

durus_DIVs <- psmelt(env_ps) %>%
  filter(!str_detect(Culture_genus, "Breviolum|Cladocopium|Effrenium"))  %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|") %>%
  filter(ASV_Species %in% Durusdinium_top_3_ASV$ASV_Species) %>%
  mutate(ASV_Species = fct_drop(ASV_Species))

fugacium_DIVs <- psmelt(env_ps) %>%
  filter(!str_detect(Culture_genus, "Breviolum|Cladocopium|Effrenium")) %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|") %>%
  filter(ASV_Species %in% Fugacium_top_3_ASV$ASV_Species) %>%
  mutate(ASV_Species = fct_drop(ASV_Species))

# Others

bardf_other <- psmelt(env_ps) %>%
  filter(!str_detect(Culture_genus, "Breviolum|Cladocopium|Effrenium"))  %>%
    mutate(Species = as.character(Species)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
         TRUE ~ Species)) %>%
    unite(OTU, Species, col = "ASV_Species", sep = "|") %>%
  filter(!(ASV_Species %in% Symbiodinium_top_3_ASV$ASV_Species)) %>%
  filter(!(ASV_Species %in% Durusdinium_top_3_ASV$ASV_Species)) %>%
  filter(!(ASV_Species %in% Fugacium_top_3_ASV$ASV_Species)) %>%
  mutate(ASV_Species = as.character(ASV_Species)) %>%
  mutate(ASV_Species = case_when(Genus == "Symbiodinium" ~ "Other_Symbiodinium",
                             Genus == "Durusdinium" ~ "Other_Durusdinium",
                             Genus == "Fugacium" ~ "Other_Fugacium",
                             TRUE ~ "Other_Symbiodiniaceae"),
         ASV_Species = case_when(Genus == "Symbiodinium" ~ "Other_Symbiodinium",
                         Genus == "Durusdinium" ~ "Other_Durusdinium",
                         Genus == "Fugacium" ~ "Other_Fugacium",
                             TRUE ~ "Other_Symbiodiniaceae"))

other_pal <- c("#5A5A5A", "#9E9E9E", "#DFDFDF", "#FFFFFF")
names(other_pal) <- c("Other_Fugacium","Other_Symbiodinium","Other_Durusdinium","Other_Symbiodiniaceae")

#-----------

# All colour palettes

all_pal <- c(CCMP_2430_pal, CCMP_2461_pal, CCMP_2469_pal, CCMP_2548_pal, Cult_24_Sugget_pal, CCMP_2592_pal, Cult_28_Sugget_pal, Cult_29_Sugget_pal, Durusdinium_pal, CCMP_2434_pal, Cult_133_pal, Cult_135_pal, other_pal)

# Final bardf

bardf <- rbind(symbio_DIVs, durus_DIVs, fugacium_DIVs, bardf_other) %>%
    filter(Sequenced_genus == Genus | Sequenced_genus == "x") %>%
  mutate(Plot_specific = case_when(str_detect(Specific, "Sediment|Water|Macroalgae") ~ Specific,
                                   TRUE ~ Culture_genus)) %>%
  mutate(Plot_specific = fct_relevel(Plot_specific, "Fugacium", "Water", "Symbiodinium", "Sediment", "Durusdinium",  "Macroalgae")) %>%
  mutate(label = paste0(Site, ".", Replicate)) %>%
  mutate(Sample = as.character(Sample)) %>%
  mutate(label = case_when(label == "x.x" ~ Sample, TRUE ~ label)) %>%
  mutate(label = fct_relevel(label, "Cult_133", "CCMP_2434", "Cult_135", "CCMP_2430", "CCMP_2461", "CCMP_2469", "CCMP_2548", "Cult_24_Sugget", "CCMP_2592", "Cult_28_Sugget", "Cult_29_Sugget", "CCMP_2556", "RB7", "Cult_RD03")) %>%
  mutate(ASV_Species = fct_relevel(ASV_Species, "ASV19|F1_AF184946", "ASV299|F1_AF184946", "ASV405|F1_AF184946", "ASV15|F_AF333516", "ASV25|F_AF333516", "ASV457|F_AF333516",  "ASV334|F_AF333516", "ASV953|F_AF333516", "Other_Fugacium", "ASV34|A3_DQ838546", "ASV203|A3_DQ838546", "ASV1006|A3_DQ838546", "ASV24|A_AF184942", "ASV712|A_AF184942", "ASV965|A_AF184942", "ASV32|A1.1_AF333504", "ASV234|A1.1_AF333504", "ASV301|A1.1_AF333504", "ASV18|A_AF184948", "ASV471|A_AF184948", "ASV436|A_AF184948", "ASV510|A_AF184948", "ASV28|A5_AF333508", "ASV472|A5_AF333508", "ASV668|A5_AF333508", "ASV39|A_DQ174724", "ASV41|A_DQ174724", "ASV520|A_DQ174724", "ASV29|A1_AB097463", "ASV163|A1_AB097463", "ASV341|A1_AB097463", "Other_Symbiodinium", "ASV17|D1_DQ838545", "ASV36|D1a_AF499802", "ASV102|D4-5_EU812743", "ASV251|D1a_AF499802", "ASV117|D1a_AF499802", "Other_Durusdinium", "Other_Symbiodiniaceae")) %>%
  ungroup() %>%
  group_by(Sample, Specific, Season, Plot_specific, label, ASV_Species) %>%
  summarise(Abundance = sum(Abundance)) %>%
  ungroup()
```

## Figure 3

```{r}
ggplot(bardf, aes(x = label, y = Abundance)) +
    geom_bar(stat = "identity", aes(fill = ASV_Species), position = "fill") +
    facet_wrap(~Plot_specific * Season, scales = "free_x", ncol = 3) +
    scale_y_continuous(labels = scales::percent) +
    theme(aspect.ratio = 1, legend.position = "right") +
    guides(fill = guide_legend(ncol = 1)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "left") +
    scale_fill_manual(values = all_pal) +
    ylab("Relative Abundance (%)")
```

## Fugacium, Symbiodinium, Durusdinium DIV summary statistics

```{r}
FSD_ss <- bardf %>%
  filter(Abundance > 0) %>%
  group_by(Sample) %>%
  mutate(Abundance_rel = (Abundance/sum(Abundance))*100) %>%
  ungroup() %>%
  mutate(ASV_Species = as.character(ASV_Species),
    group = case_when(str_detect(ASV_Species, "ASV") ~ "DIV", TRUE ~ ASV_Species)) %>%
  group_by(Sample, Specific, Season, ASV_Species) %>%
  summarise(abund = sum(Abundance_rel))
```

# Remaining sequences that are without material for DIVs

```{r}
sym_only <- ps %>% psmelt() %>%
  filter(Type == "Host") %>%
    filter(Abundance > 0)

not_DIV <- ps %>% psmelt() %>%
  filter(Type != "Host") %>%
  filter(Type != "Culture") %>%
  filter(!(OTU %in% sym_only$OTU)) %>%
    mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"))) %>%
  unite(OTU, Species, col = "ASV_Species", sep = "|") %>%
  filter(!(ASV_Species %in% names(all_pal))) %>%
  filter(Abundance > 0)

remaining_df <- ps_filt %>%
  psmelt() %>%
  mutate(Genus = fct_relevel(Genus, c("Cladocopium", "Halluxium", "Symbiodinium_Fr2", "Freudenthalidium", "Symbiodinium_Fr4", "Fugacium", "Breviolum", "Symbiodinium_I", "Foraminifera_D", "Durusdinium", "Gerakladium", "Symbiodinium")),
        Specific = fct_relevel(Specific, c("Water", "Sediment", "Macroalgae"))) %>%
  filter(Type == "Environment") %>%
  mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"))) %>%
  unite(OTU, Species, col = "ASV_Species", sep = "|", remove = FALSE) %>%
  filter(ASV_Species %in% not_DIV$ASV_Species) %>%
  filter(Abundance > 0) %>%
  group_by(Sample, Genus) %>%
  top_n(., 1, Abundance) %>%
  ungroup() %>%
  mutate(ASV_Species = fct_drop(ASV_Species)) %>%
  group_by(Sample) %>%
  mutate(Abundance_rel = (Abundance/sum(Abundance))*100) %>%
  ungroup()
```

## Figure 4a

```{r}
Fig4a <- remaining_df %>%
  group_by(Specific, Genus, Season) %>%
  summarise(Abundance = mean(Abundance)) %>%
    ggplot(aes(x = Specific, y = Abundance)) +
          geom_bar(stat = "identity", aes(fill = Genus), position = "fill") +
          facet_wrap(~Season, scales = "free_x", ncol = 1) +
          scale_y_continuous(labels = scales::percent) +
          theme(aspect.ratio = 1, legend.position = "left") +
          theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "left") +
          scale_fill_manual(values = genus_cols) +
          ylab("Relative Abundance")

rdf_ss <- remaining_df %>%
  group_by(Specific, Genus, Season) %>%
  summarise(Abundance = mean(Abundance)) %>%
  ungroup() %>%
  group_by(Specific, Season) %>%
  mutate(abund_rel = Abundance/sum(Abundance)*100)
```

## ASV sequence similarity network

```{r}
get_long_kdist <- function(refdb = "filepath", phyloseq = ps, k = 7, taxalist = taxnames){
  
  allTaxa <- taxa_names(ps)
  allTaxa <- allTaxa %in% taxalist
  ps_filt <- prune_taxa(allTaxa, ps)
  
  taxlist <- as.data.frame(tax_table(ps_filt)) %>%
    tibble::rownames_to_column(var = "ASV") %>%
  select(ASV, Genus, Species) %>%
  distinct(Species, .keep_all = TRUE) %>%
  mutate(Species = as.character(Species))

  ASV <- refseq(ps_filt) %>%
    DNAStringSet_to_df()
  
  SDB <- readDNAStringSet(refDB) %>%
    DNAStringSet_to_df() %>%
    mutate(names = str_remove(names, "Eukaryota;Dinoflagellata;Dinophyceae;Suessiales;Symbiodiniaceae;")) %>%
    separate(names, into = c("Genus","names"), sep = ";") %>%
    filter(names %in% taxlist$Species)
  
  SDB_bind <- SDB %>%
    select(names, seqs)
  
  SDB_ASV_seqs <- rbind(SDB_bind, ASV)
  
  kdist <- SDB_ASV_seqs %>%
    df_to_DNAStringset() %>%
    DNAStringSet_to_DNAbin() %>%
    kdistance(k = k, residues = "DNA", method = "edgar") %>%
    as.matrix()
  
  long_dist <- melt(kdist)[melt(lower.tri(kdist))$value,] %>%
    mutate(value = (1-value)*100) %>%
    select(from = Var1, to = Var2, kdist = value)
  
  taxgen <- as.data.frame(tax_table(ps_filt)) %>%
    tibble::rownames_to_column(var = "ASV") %>%
    select(ASV, Genus)
  SDB_gen <- SDB %>% select(ASV = names, Genus)
  genus_list <- rbind(taxgen, SDB_gen)

  long_dist <- left_join(long_dist, genus_list, by = c("from" = "ASV")) %>%
    full_join(., genus_list, by = c("to" = "ASV")) %>%
    filter(Genus.x == Genus.y) %>%
    select(from, to, kdist, Genus = Genus.x)
  
  return(long_dist)
}

get_network_data <- function(refdb = "filepath", phyloseq = ps, taxalist = taxa_names){
  
  allTaxa <- taxa_names(ps)
  allTaxa <- allTaxa %in% taxalist
  ps_filt <- prune_taxa(allTaxa, ps)
  
  taxlist <- as.data.frame(tax_table(ps_filt)) %>%
  select(Species) %>%
  distinct(Species) %>%
  mutate(Species = as.character(Species))
  
  ASVdata <- enframe(taxa_sums(ps_filt)) %>%
    select(names = name, abundance = value) %>%
    mutate(abundance = (abundance/sum(abundance))*100) %>%
    mutate(origin = "ASV")
  
  genuslist <- as.data.frame(tax_table(ps_filt)) %>%
    tibble::rownames_to_column(var = "names") %>%
    select(names, Genus)
  
  ASVdata <- left_join(ASVdata, genuslist)
  
  SDB <- readDNAStringSet(refDB) %>%
    DNAStringSet_to_df() %>%
    mutate(names = str_remove(names, "Eukaryota;Dinoflagellata;Dinophyceae;Suessiales;Symbiodiniaceae;")) %>%
    separate(names, into = c("Genus","names"), sep = ";") %>%
    filter(names %in% taxlist$Species)
  
  SDBdata <- SDB %>%
    select(names, Genus) %>%
    mutate(abundance = mean(ASVdata$abundance),
           origin = "Reference") %>%
    select(names, abundance, origin, Genus)
  
  network_data <- rbind(SDBdata, ASVdata)
  
  return(network_data)
}

refDB <- "../../Raw_data/Reference_databases/ITS2dbn1_Dinophy_Symbio.fasta"

full_names <- (remaining_df %>% distinct(OTU))$OTU
full_names_kdist <- get_long_kdist(refdb = refDB, phyloseq = ps_filt, taxalist = full_names) %>%
      mutate(from = case_when(str_detect(from, "|") ~ word(as.character(from), 1, sep = "\\|"),
         TRUE ~ from),
         to = case_when(str_detect(to, "|") ~ word(as.character(to), 1, sep = "\\|"),
         TRUE ~ to))
full_names_network <- get_network_data(refdb = refDB, phyloseq = ps_filt, taxalist = full_names) %>%
  mutate(names = case_when(str_detect(names, "|") ~ word(as.character(names), 1, sep = "\\|"),
         TRUE ~ names))
```

## Figure 4b

```{r}
Fig4b <- tbl_graph(nodes = full_names_network, edges = full_names_kdist) %>%
          activate(edges) %>%
          filter(kdist > 96) %>%
          activate(nodes) %>%
          filter(abundance > 0) %>%
          ggraph(layout = "fr") + 
          geom_edge_link(alpha = 0.4, aes(width = kdist)) + 
          scale_edge_width(range = c(0.4, 2.5)) +
          geom_node_point(aes(fill = Genus, shape = origin, size = abundance)) +
          scale_shape_manual(values = c(21, 22)) +
          scale_size_area(max_size = 17) +
          geom_node_text(aes(label = names), size = 3, repel = TRUE) +
          scale_fill_manual(values = genus_cols) +
          theme(aspect.ratio = 1, legend.position = "right")
```

## Figure 4

```{r}
Fig4a + Fig4b
```

## Remaining summary counts

```{r}
R_ss <- remaining_df %>%
  filter(Abundance > 0) %>%
  group_by(Sample) %>%
  mutate(Abundance_rel = (Abundance/sum(Abundance))*100) %>%
  ungroup()

R_ss <- remaining_df %>%
  filter(Abundance > 0) %>%
  group_by(Specific, Season, Genus) %>%
  summarise(abund = sum(Abundance)) %>%
  mutate(Abundance_rel = (abund/sum(abund))*100) %>%
  ungroup()
```

## Reviewer 1 wanted similarities in terms of bp

Code chunk below to quickly align study and ref seqs and count mismatches

```{r}
SDB <- readDNAStringSet("../../Raw_data/Reference_databases/ITS2dbn1_Dinophy_Symbio.fasta") %>%
    DNAStringSet_to_df() %>%
    mutate(names = str_remove(names, "Eukaryota;Dinoflagellata;Dinophyceae;Suessiales;")) %>%
    separate(names, into = c("Family", "Genus","names"), sep = ";") %>%
    filter(Family == "Symbiodiniaceae") %>%
    select(names, seqs)

targets <- c("ASV394", "G3_AM748600")
bind_ref_study <- refseq(ps) %>%
  DNAStringSet_to_df()
ref_study <- rbind(bind_ref_study, SDB)
target_seqs <- ref_study %>%
  filter(names %in% targets) %>%
  df_to_DNAStringset() %>% 
  AlignSeqs() %>%
  DNAStringSet_to_df()
A <- melt(str_split(target_seqs$seqs[1], ""))
B <- melt(str_split(target_seqs$seqs[2], ""))
match_tab <- data.frame(A = (A$value), B = (B$value))
match_tab <- match_tab %>% 
  mutate(A = as.character(A), B = as.character(B)) %>%
  mutate(match = case_when(A == B ~ "match", TRUE ~ "no match"))

sum(match_tab$match == "no match", na.rm = TRUE)
```


# Differential abundance

## Niche

```{r}
ps_ds <- ps %>%
  subset_samples(Type != "Culture") %>%
  subset_samples(Type != "Host")

ps_ds <- tax_glom(ps_ds, taxrank = "Genus")

gm_mean = function(x, na.rm = TRUE){exp(sum(log(x[x > 0]), na.rm = na.rm) / length(x))}

alpha <- 0.05

restax <- as.data.frame(ps_ds@tax_table@.Data)
restax <- rownames_to_column(restax, var = "ASVID")

# Compare across niches
ps_gen_ds2 <- phyloseq_to_deseq2(ps_ds, ~ Specific)
geoMeans <- apply(counts(ps_gen_ds2), 1, gm_mean)
estszef <- estimateSizeFactors(ps_gen_ds2, geoMeans = geoMeans)
ps_gen_ds2 <- DESeq(estszef, fitType = "parametric")

res.w.s <- results(ps_gen_ds2, cooksCutoff = FALSE, contrast = c("Specific", "Water", "Sediment"), tidy = TRUE) %>%
  filter(padj < alpha) %>%
  left_join(., restax, by = c("row" = "ASVID")) %>%
  mutate(test = "Water_v_Sediment")

res.w.m <- results(ps_gen_ds2, cooksCutoff = FALSE, contrast = c("Specific", "Water", "Macroalgae"), tidy = TRUE) %>%
  filter(padj < alpha) %>%
  left_join(., restax, by = c("row" = "ASVID")) %>%
  mutate(test = "Water_v_Macroalgae")

res.s.m <- results(ps_gen_ds2, cooksCutoff = FALSE, contrast = c("Specific", "Sediment", "Macroalgae"), tidy = TRUE) %>%
  filter(padj < alpha) %>%
  left_join(., restax, by = c("row" = "ASVID")) %>%
  mutate(test = "Sediment_v_Macroalgae")

res_all <- rbind(res.w.s, res.w.m, res.s.m)
```

## Season

```{r}
ps_ds <- ps %>%
  subset_samples(Type != "Culture") %>%
  subset_samples(Type != "Host")

ps_ds <- tax_glom(ps_ds, taxrank = "Genus")

gm_mean = function(x, na.rm = TRUE){exp(sum(log(x[x > 0]), na.rm = na.rm) / length(x))}

alpha <- 0.05

restax <- as.data.frame(ps_ds@tax_table@.Data)
restax <- rownames_to_column(restax, var = "ASVID")

# Compare across niches
ps_gen_ds2 <- phyloseq_to_deseq2(ps_ds, ~ Season)
geoMeans <- apply(counts(ps_gen_ds2), 1, gm_mean)
estszef <- estimateSizeFactors(ps_gen_ds2, geoMeans = geoMeans)
ps_gen_ds2 <- DESeq(estszef, fitType = "parametric")

res.s.s <- results(ps_gen_ds2, cooksCutoff = FALSE, contrast = c("Season", "Spawning", "Summer"), tidy = TRUE) %>%
  filter(padj < alpha) %>%
  left_join(., restax, by = c("row" = "ASVID")) %>%
  mutate(test = "Spawning_v_Summer")
```

```{r}
write.csv(rbind(res_all, res.s.s), "differential_abundance.csv")
```

# Effrenium

In Sweet et al 2014 (https://onlinelibrary.wiley.com/doi/full/10.1111/maec.12092), Effrenium was reported at HI.

I want to check if this sequence is actually Effrenium as we do not find a single Effrenium sequence in the present study.

```{r}
library(rentrez)
library(alignfigR)

## Retrieve these from genbank
query <- c("JN406301", "JN406302") # Some have trailing white space - use trimws() to remove it

# Set my API key
set_entrez_key("XXXXXXXXXXXXXXXXXXXXXXXXX")

# Call fetch_seqs and send all output to fasta
# Note: this appends to the geosymbio_all.fasta file so if you stop the script halfway through, delete the file before restarting.

for(i in 1:length(query)){
	q <- query[i]
	seq <- fetch_seqs(q)
	cat(seq, file = "Sweet_Effrenium.fasta", append = TRUE)
	Sys.sleep(0.5) # Wait between calls so we dont get IP banned by NCBI :(
}

# Check result versus query and check if any seqs were missing from the DB
Sweet_E <- readDNAStringSet("Sweet_Effrenium.fasta") %>%
  DNAStringSet_to_df()

SDB <- readDNAStringSet("../../Raw_data/Reference_databases/ITS2dbn1_Dinophy_Symbio.fasta") %>%
  DNAStringSet_to_df() %>%
  filter(str_detect(names, "Effrenium"))

Sweet_SDB <- rbind(Sweet_E, SDB) %>%
  df_to_DNAStringset() %>%
  AlignSeqs() %>%
  writeXStringSet("Sweet_SDB_Effrenium_aligned.fasta")

# Sequences fail to align for the most part...
Sweet_SDB_aligned <- read_alignment("Sweet_SDB_Effrenium_aligned.fasta")
plot_alignment(Sweet_SDB_aligned, palette = "DNA", taxa = names(Sweet_SDB_aligned))

Sweet_SDB <- rbind(Sweet_E, SDB) %>%
  df_to_DNAStringset() %>%
  DNAStringSet_to_DNAbin() %>%
  kdistance(k = 7, method = "edgar") %>%
  as.matrix()

Sweet_SDB_long <- melt(Sweet_SDB)[melt(lower.tri(Sweet_SDB))$value,] %>%
  mutate(value = (1-value)*100) %>%
  select(from = Var1, to = Var2, kdist = value)

# Share only up to 20% similarity with other Effrenium sequences. My suggestion is this is sequence does not belong to the Symbiodiniaceae after further BLAST searches on NCBI.
```


