---
title: "qPCR"
author: "MNitschke"
date: "19/05/2020"
output: html_document
---

```{r}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(patchwork)
```

# qPCR count data import

```{r}
data <- read_csv("qpcr_cells_cm3.csv") %>%
    mutate(Site = as.factor(Site),
         Habitat = fct_relevel(Habitat, "Water", "Sediment", "Macroalgae")) %>%
    unite(Habitat, Season, col = "Habitat_Season", sep = " ", remove = FALSE) %>%
    unite(Year, Season, Habitat, Site, Replicate, Genus, col = "Full_label", sep = "_", remove = FALSE) %>%
    mutate(Habitat_Season = fct_relevel(Habitat_Season, c("Water Spawning", "Water Summer", "Sediment Spawning", "Sediment Summer", "Macroalgae Spawning", "Macroalgae Summer")))
```

# Two-way ANOVA

```{r}
# Identify outliers
data_out <- data %>%
  group_by(Habitat, Season, Genus) %>%
  identify_outliers(Cells_cm3) %>%
  filter(is.extreme == TRUE)

# Remove outliers
data_no <- data %>%
  filter(!(Full_label %in% data_out$Full_label)) # Remove extreme outliers

# Summary statistics
data_ss <- data_no %>%
  group_by(Habitat, Genus) %>%
  get_summary_stats(Cells_cm3, type = "mean_sd")

data_ss <- data_no %>%
  group_by(Season, Genus) %>%
  get_summary_stats(Cells_cm3, type = "mean_sd")

data_ss <- data_no %>%
  group_by(Habitat, Season, Genus) %>%
  get_summary_stats(Cells_cm3, type = "mean_sd")

# Create a QQ plot of residuals - all points fall approximately along the line - normality was 
ggqqplot(data_no %>% filter(Genus == "Cladocopium"), "Cells_cm3", ggtheme = theme_bw()) +
  facet_grid(Habitat ~ Season)
ggqqplot(data_no %>% filter(Genus == "Durusdinium"), "Cells_cm3", ggtheme = theme_bw()) +
  facet_grid(Habitat ~ Season)
ggqqplot(data_no %>% filter(Genus == "Symbiodinium"), "Cells_cm3", ggtheme = theme_bw()) +
  facet_grid(Habitat ~ Season)

# Levenes test of Homogeneity - all tests fail
data_no %>%
  filter(Genus == "Cladocopium") %>% 
  levene_test(Cells_cm3 ~ Habitat * Season)

data_no %>%
  filter(Genus == "Durusdinium") %>% 
  levene_test(Cells_cm3 ~ Habitat * Season)

data_no %>%
  filter(Genus == "Symbiodinium") %>% 
  levene_test(Cells_cm3 ~ Habitat * Season)

# Try log-transforming - all tests still fail

data_no %>%
  filter(Genus == "Cladocopium") %>%
  mutate(log_Cells_cm3 = log(Cells_cm3)) %>%
  levene_test(log_Cells_cm3 ~ Habitat * Season)

data_no %>%
  filter(Genus == "Durusdinium") %>% 
  mutate(log_Cells_cm3 = log(Cells_cm3)) %>%
  levene_test(log_Cells_cm3 ~ Habitat * Season)

data_no %>%
  filter(Genus == "Symbiodinium") %>% 
  mutate(log_Cells_cm3 = log(Cells_cm3)) %>%
  levene_test(log_Cells_cm3 ~ Habitat * Season)

# There are no non-parametric equivalents to a two-way ANOVA. So instead, we will use a welch one way test (does not assume equal variances) for Habitat and Season, separately
```

## Habitat - Welch Anova test & Games Howell test

```{r}
res_welch_c <- data_no %>%
  filter(Genus == "Cladocopium") %>% 
  welch_anova_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Cladocopium")

res_welch_d <- data_no %>%
  filter(Genus == "Durusdinium") %>% 
  welch_anova_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Durusdinium")

res_welch_s <- data_no %>%
  filter(Genus == "Symbiodinium") %>% 
  welch_anova_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Symbiodinium")

welch_res_hab <- rbind(res_welch_c, res_welch_d, res_welch_s)

res_welch_c_pwc <- data_no %>%
  filter(Genus == "Cladocopium") %>%
  games_howell_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Cladocopium")

res_welch_d_pwc <- data_no %>%
  filter(Genus == "Durusdinium") %>%
  games_howell_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Durusdinium")

res_welch_s_pwc <- data_no %>%
  filter(Genus == "Symbiodinium") %>%
  games_howell_test(Cells_cm3 ~ Habitat) %>%
  mutate(genus = "Symbiodinium")

gh_res_hab <- rbind(res_welch_c_pwc, res_welch_d_pwc, res_welch_s_pwc)
```

## Season - Welch Anova test & Games Howell test

```{r}
res_welch_c_w <- data_no %>%
  filter(Genus == "Cladocopium") %>%
  filter(Habitat == "Water") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Cladocopium_water")

res_welch_d_w <- data_no %>%
  filter(Genus == "Durusdinium") %>%
    filter(Habitat == "Water") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Durusdinium_water")

res_welch_s_w <- data_no %>%
  filter(Genus == "Symbiodinium") %>%
    filter(Habitat == "Water") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Symbiodinium_water")

# res_welch_c <- data_no %>%
#   filter(Genus == "Cladocopium") %>%
#   filter(Habitat == "Sediment") %>%
#   welch_anova_test(Cells_cm3 ~ Season) %>%
#   mutate(genus = "Cladocopium")

# res_welch_d <- data_no %>%
#   filter(Genus == "Durusdinium") %>%
#     filter(Habitat == "Sediment") %>%
#   welch_anova_test(Cells_cm3 ~ Season) %>%
#   mutate(genus = "Durusdinium")

res_welch_s_s <- data_no %>%
  filter(Genus == "Symbiodinium") %>%
    filter(Habitat == "Sediment") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Symbiodinium_sediment")

res_welch_c_m <- data_no %>%
  filter(Genus == "Cladocopium") %>%
  filter(Habitat == "Macroalgae") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Cladocopium_macroalgae")

res_welch_d_m <- data_no %>%
  filter(Genus == "Durusdinium") %>%
    filter(Habitat == "Macroalgae") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Durusdinium__macroalgae")

res_welch_s_m <- data_no %>%
  filter(Genus == "Symbiodinium") %>%
    filter(Habitat == "Macroalgae") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Symbiodinium__macroalgae")

welch_res_seas <- rbind(res_welch_c_w, res_welch_d_w, res_welch_s_w, res_welch_s_s, res_welch_c_m, res_welch_d_m, res_welch_s_m)
```

```{r}
res_welch_c <- data_no %>%
  filter(Genus == "Cladocopium") %>%
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Cladocopium")

res_welch_d <- data_no %>%
  filter(Genus == "Durusdinium") %>% 
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Durusdinium")

res_welch_s <- data_no %>%
  filter(Genus == "Symbiodinium") %>% 
  welch_anova_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Symbiodinium")

welch_res_seas <- rbind(res_welch_c, res_welch_d, res_welch_s)

res_welch_c_pwc <- data_no %>%
  filter(Genus == "Cladocopium") %>%
  games_howell_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Cladocopium")

res_welch_d_pwc <- data_no %>%
  filter(Genus == "Durusdinium") %>%
  games_howell_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Durusdinium")

res_welch_s_pwc <- data_no %>%
  filter(Genus == "Symbiodinium") %>%
  games_howell_test(Cells_cm3 ~ Season) %>%
  mutate(genus = "Symbiodinium")

gh_res_seas <- rbind(res_welch_c_pwc, res_welch_d_pwc, res_welch_s_pwc)
```


# Figure 5

```{r}
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

ggplot(data_no, aes(Habitat_Season, Cells_cm3, fill = Habitat_Season)) +
          geom_boxplot() +
          facet_wrap(~Genus, ncol = 1) +
          stat_summary(fun.data = give.n, geom = "text", position = position_nudge(y = 1)) +
          scale_shape_manual(values = c(21,22)) +
          scale_y_log10(breaks=c(.01,.1,1,10,100,1000)) +
          theme(aspect.ratio = 1) +
          theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "none") +
          scale_fill_manual(values = c("#BCD6E9", "#1F77B4FF", "#FFD9B7", "#FF7F0EFF", "#C0E3C0", "#2CA02CFF"))
```

# -------------------------------------------
# OLD CODE BELOW
# Phyloseq data import

```{r}
# ps <- readRDS("../dada2_Heron/phyloseq.rds") %>%
#   subset_samples(Heron_study == "y")
# 
# # Clean data
# ps <- ps %>% # Keep only samples for Heron Island study
#   subset_taxa(Family == "Symbiodiniaceae") # Remove ITS2 sequences not assigned to Symbiodiniaceae
# 
# # Clean up low-depth samples and low-abundance ASVs
# ps <- prune_samples(sample_sums(ps) >= 250, ps)
# ps <- prune_taxa(taxa_sums(ps) > 1, ps)
```

## ASV relative abundance of Cladocopium, Durusdinium, and Symbiodinium

```{r}
# bar_df <- ps %>%
#   psmelt() %>%
#   filter(Type == "Environment") %>%
#   filter(Genus == "Symbiodinium" | Genus == "Durusdinium" | Genus == "Cladocopium") %>%
#   mutate(Genus = fct_relevel(Genus, c("Cladocopium", "Durusdinium", "Symbiodinium"))) %>%
#   filter(Abundance > 0) %>%
#   mutate(Genus = fct_drop(Genus)) %>%
#   mutate(Species = as.character(Species)) %>%
#   mutate(Species = case_when(str_detect(Species, "|") ~ word(as.character(Species), 1, sep = "\\|"),
#          TRUE ~ Species)) %>%
#   unite(OTU, Species, col = "ASV_Species", sep = "|", remove = FALSE) %>%
#   unite(Specific, Season, col = "Specific_Season", sep = " ", remove = FALSE) %>%
#   mutate(Specific_Season = as.factor(Specific_Season)) %>%
#   mutate(Specific_Season = fct_relevel(Specific_Season, c("Water Spawning", "Water Summer", "Sediment Spawning", "Sediment Summer", "Macroalgae Spawning", "Macroalgae Summer"))) %>%
#   arrange(Genus, Species) %>%
#   mutate(ASV_Species = fct_inorder(ASV_Species)) %>%
#   group_by(Specific_Season, Genus, ASV_Species) %>%
#   summarise(Abundance = sum(Abundance)) %>%
#   ungroup()
```

```{r}
# Fig5b <- ggplot(data = bar_df, aes(x = Specific_Season, y = Abundance)) +
#           geom_bar(stat = "identity", aes(fill = ASV_Species), position = "fill", colour = "black") + 
#           scale_y_continuous(labels = scales::percent) +
#           facet_wrap(~Genus, ncol = 3) +
#           theme(aspect.ratio = 1) +
#           guides(fill = guide_legend(ncol = 3)) +
#           theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), legend.position = "none") +
#           ylab("Relative Abundance of ASVs")
```

# Figure 5

```{r}
# Fig5a / Fig5b
```

# Figure 5 Statistics

# Controling for count of unique ASVs

```{r}
# ps_filt <- subset_samples(ps, Type == "Environment")
# 
# # Cladocopium
# Clado <- ps_filt %>%
#   psmelt() %>%
#   filter(Abundance > 0) %>%
#   filter(Genus == "Cladocopium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Unique_ASVs = n_distinct(OTU)) %>%
#   ungroup()
# Clado_complete <- Clado %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Unique_ASVs = 0)) %>%
#   mutate(Genus = "Cladocopium")
# 
# # Durusdinium
# Dur <- ps_filt %>%
#   psmelt() %>%
#   filter(Abundance > 0) %>%
#   filter(Genus == "Durusdinium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Unique_ASVs = n_distinct(OTU)) %>%
#   ungroup()
# Dur_complete <- Dur %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Unique_ASVs = 0)) %>%
#   mutate(Genus = "Durusdinium")
# 
# # Symbiodinium
# Sym <- ps_filt %>%
#   psmelt() %>%
#   filter(Abundance > 0) %>%
#   filter(Genus == "Symbiodinium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Unique_ASVs = n_distinct(OTU)) %>%
#   ungroup()
# Sym_complete <- Clado %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Unique_ASVs = 0)) %>%
#   mutate(Genus = "Symbiodinium")
# 
# # Combined
# ASV_richness <- rbind(Clado_complete, Dur_complete, Sym_complete) %>%
#   mutate(Site = str_remove(Site, "Site_")) %>%
#   mutate(Site = as.factor(Site)) %>%
#   select(Season, Site, Habitat = Specific, Replicate, Genus, Unique_ASVs)
# 
# # ANCOVA data frame
# 
# unique_ASV_data <- left_join(ASV_richness, data)
```

## Controling for Genus-specific ASV abundances

```{r}
# ps_filt <- subset_samples(ps, Type == "Environment")
# 
# # Cladocopium
# Clado <- ps_filt %>%
#   psmelt() %>%
#   filter(Genus == "Cladocopium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Genus_Sum = sum(Abundance)) %>%
#   ungroup()
# Clado_complete <- Clado %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Genus_Sum = 0)) %>%
#   mutate(Genus = "Cladocopium")
# 
# # Durusdinium
# Dur <- ps_filt %>%
#   psmelt() %>%
#   filter(Abundance > 0) %>%
#   filter(Genus == "Durusdinium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Genus_Sum = sum(Abundance)) %>%
#   ungroup()
# Dur_complete <- Dur %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Genus_Sum = 0)) %>%
#   mutate(Genus = "Durusdinium")
# 
# # Symbiodinium
# Sym <- ps_filt %>%
#   psmelt() %>%
#   filter(Abundance > 0) %>%
#   filter(Genus == "Symbiodinium") %>%
#   group_by(Specific, Season, Site, Replicate) %>%
#   summarise(Genus_Sum = sum(Abundance)) %>%
#   ungroup()
# Sym_complete <- Clado %>%
#   complete(Specific, Season, Site, Replicate, fill = list(Genus_Sum = 0)) %>%
#   mutate(Genus = "Symbiodinium")
# 
# # Combined
# Genus_counts <- rbind(Clado_complete, Dur_complete, Sym_complete) %>%
#   mutate(Site = str_remove(Site, "Site_")) %>%
#   mutate(Site = as.factor(Site)) %>%
#   select(Season, Site, Habitat = Specific, Replicate, Genus, Genus_Sum)
# 
# # ANCOVA data frame
# 
# Genus_count_data <- inner_join(data, Genus_counts)
```

```{r}
# complete_data <- left_join(Genus_count_data, unique_ASV_data)
```

## Cladocopium ANCOVA

### Assumptions

```{r}
# complete_data_no <- complete_data %>% filter(Cells_cm3 < 3000) # There is one sample outlier with 10x the cells_cm3 of next closest sample
# 
# ggscatter(complete_data_no %>% filter(Genus == "Cladocopium"),
#   x = "Cells_cm3", y = "Unique_ASVs",
#   facet.by  = c("Habitat", "Season"), 
#   short.panel.labs = FALSE
#   ) +
#   stat_smooth(method = "loess", span = 0.9)
# 
# complete_data %>%
#   filter(Genus == "Cladocopium") %>%
#   anova_test(Cells_cm3 ~ Habitat_Season * Unique_ASVs)
# # There is homogeneity of regression slopes as the interaction terms, between the covariate (Unique_ASVs) and grouping variables (Habitat and Season), is not statistically significant, p > 0.05.
# 
# # Fit the model, the covariate goes first
# model <- lm(Cells_cm3 ~ Unique_ASVs + Habitat*Season, data = complete_data %>% filter(Genus == "Cladocopium"))
# 
# # Inspect the model diagnostic metrics 
# model.metrics <- augment(model) %>%
#   select(-.hat, -.sigma, -.fitted, -.se.fit) # Remove details
# head(model.metrics, 9)
# 
# shapiro_test(model.metrics$.resid)
# levene_test(.resid ~ Habitat*Season, data = model.metrics)
# 
# complete_data %>%
#   filter(Genus == "Cladocopium") %>%
#   anova_test(Cells_cm3 ~ Unique_ASVs + Habitat * Season)
```

```{r}
# ggplot(complete_data_no, aes(Cells_cm3, Unique_ASVs)) +
#   geom_point(size = 3) +
#   stat_smooth(method = "lm", span = 0.9) +
#   facet_wrap(~Habitat*Season, scales = "free")
```